Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-21 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:21	15:21:10	(Fri21.Aug)

@@

\begin{figure*}[tbhp!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{Typical frequency responses for windows computed by a robust MVDR.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\newline
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{Window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight.} }\label{mvdr_selected_windows}
\end{figure*}

@@

oversampled 10 times in azimuth~\cite{Asen2014}.

>>>>

Adaptive beamformers process each pixel in a different way in an attempt to surpass the conventional limit of resolution and noise suppression. This non-linear processing of the image increases its bandwidth and introduces a need for oversampling. For MVDR a lateral oversampling factor of up to 10 times is often needed to ensure spatial shift-invariance~\cite{Asen2014}.

@@

\begin{figure*}[tbhp!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{Typical frequency responses for windows computed by a robust MVDR.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\newline
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{Window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The responses are overlayed each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight.} }\label{mvdr_selected_windows}
\end{figure*}

@@
